Trends of SDR in Thessaloniki

### 2023-11-03 MDPI_submition.Rmd
Commit 2023-11-03 10:14

There is a consensus among researchers that the major factor affecting the variability of SDR attenuation is the interactions of solar radiation with atmospheric aerosols and clouds. 
Those interactions, among other factors, have been analysed with models [@Li2016; @Samset2018], showing the existence of feedback mechanisms between the two.
Similar finds, have been showed in observational data [@Schwarz2020; @Ohvril2009; @Zerefos2009; @Xia2007 and references therein].
<!-- Sun variability: should cite that there is no significant trend found Wild2021 -->

Due to the variability of the phenomenon, and its contributing factors, there is a constant need to investigate and monitor SDR, in different sites, to estimate its magnitude, and its relation to the local conditions.
In this study, we examine the trends of SDR, with ground-based measurements at Thessaloniki, Greece for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluated and extended the dataset used by @Bais2013, applying a different algorithm for the identification of clear-/cloud-sky instances [@Reno2016; @Reno2012a], and we derive the radiation trends for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, under different sky conditions (all-sky, clear-sky and cloud-sky).

@@

<!-- CS subjectivity -->
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, in any method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of thresholds and comparisons with ideal actinometric models and statistical analysis on different signal metrics.
The CSid algorithm was calibrated with the main focus, to identify the presence of clouds on the sky dome.
Although the fine-tuning of the procedure, few marginal cases exist, that have been identified manually as false positive or false negative but cannot affect the final results of the study.

>>>>

There is a consensus among researchers that the major factor affecting the variability of SDR attenuation is the interactions of solar radiation with atmospheric aerosols and clouds. 
Those interactions, among other factors, have been analysed with models [@Li2016; @Samset2018], showing the existence of feedback mechanisms between the two.
Similar findings have been shown in observational data [@Schwarz2020; @Ohvril2009; @Zerefos2009; @Xia2007 and references therein].
<!-- Sun variability: should cite that there is no significant trend found Wild2021 -->

Due to the significant spatial and temporal variability of the trends, and the contributing factors, there is a constant need to monitor and investigate SDR in different sites in order to estimate the degree of variability,  and its relation to the local conditions.
In this study, we examine the trends of SDR, using ground-based measurements at Thessaloniki, Greece, for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluated and extended the dataset used by @Bais2013, we applied a different algorithm for the identification of clear-/cloud-sky instances [@Reno2016; @Reno2012a], and we derived the SDR trends for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, under different sky conditions (all-sky, clear-sky and cloud-sky).
Finally, we investigated the dependence of the trends on solar zenith angle and season.

@@

<!-- CS subjectivity -->
We have to note, that the definition of clear or cloudy sky, has some subjectivity, in any method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of thresholds and comparisons with ideal radiation models and statistical analysis of different signal metrics.
The CSid algorithm was calibrated with the main focus, to identify the presence of clouds on the sky.
Despite the fine-tuning of the procedure, a few marginal cases exist, that have been identified manually as false positive or false negative but cannot affect the final results of the study.

### 2023-11-03 MDPI_submition.tex
Commit 2023-11-03 10:14

There is a consensus among researchers that the major factor affecting
the variability of SDR attenuation is the interactions of solar
radiation with atmospheric aerosols and clouds. Those interactions,
among other factors, have been analysed with models
\citep{Li2016, Samset2018}, showing the existence of feedback mechanisms
between the two. Similar finds, have been showed in observational data
\citep[ and references
therein]{Schwarz2020, Ohvril2009, Zerefos2009, Xia2007}.

Due to the variability of the phenomenon, and its contributing factors,
there is a constant need to investigate and monitor SDR, in different
sites, to estimate its magnitude, and its relation to the local
conditions. In this study, we examine the trends of SDR, with
ground-based measurements at Thessaloniki, Greece for the period 1993 to
2023, as derived from a CM-21 pyranometer. We reevaluated and extended
the dataset used by \citet{Bais2013}, applying a different algorithm for
the identification of clear-/cloud-sky instances
\citep{Reno2016, Reno2012a}, and we derive the radiation trends for the
period 1993 to 2023, under different sky conditions (all-sky, clear-sky
and cloud-sky).

@@

We have to note, that the definition of what constitutes as clear or
cloudy sky, has some subjectivity, in any method of characterization. As
a result, the details of the definition are site specific, it relies on
a combination of thresholds and comparisons with ideal actinometric
models and statistical analysis on different signal metrics. The CSid
algorithm was calibrated with the main focus, to identify the presence
of clouds on the sky dome. Although the fine-tuning of the procedure,
few marginal cases exist, that have been identified manually as false
positive or false negative but cannot affect the final results of the
study.

>>>>

There is a consensus among researchers that the major factor affecting
the variability of SDR attenuation is the interactions of solar
radiation with atmospheric aerosols and clouds. Those interactions,
among other factors, have been analysed with models
\citep{Li2016, Samset2018}, showing the existence of feedback mechanisms
between the two. Similar findings have been shown in observational data
\citep[ and references
therein]{Schwarz2020, Ohvril2009, Zerefos2009, Xia2007}.

Due to the significant spatial and temporal variability of the trends,
and the contributing factors, there is a constant need to monitor and
investigate SDR in different sites in order to estimate the degree of
variability, and its relation to the local conditions. In this study, we
examine the trends of SDR, using ground-based measurements at
Thessaloniki, Greece, for the period 1993 to 2023, as derived from a
CM-21 pyranometer. We reevaluated and extended the dataset used by
\citet{Bais2013}, we applied a different algorithm for the
identification of clear-/cloud-sky instances
\citep{Reno2016, Reno2012a}, and we derived the SDR trends for the
period 1993 to 2023, under different sky conditions (all-sky, clear-sky
and cloud-sky). Finally, we investigated the dependence of the trends on
solar zenith angle and season.

@@

We have to note, that the definition of clear or cloudy sky, has some
subjectivity, in any method of characterization. As a result, the
details of the definition are site specific, it relies on a combination
of thresholds and comparisons with ideal radiation models and
statistical analysis of different signal metrics. The CSid algorithm was
calibrated with the main focus, to identify the presence of clouds on
the sky. Despite the fine-tuning of the procedure, a few marginal cases
exist, that have been identified manually as false positive or false
negative but cannot affect the final results of the study.
